---
title: "Periodical 1 AAR"
author: "ENTER YOU NAME AND ROLL (LAST Three digits)"
format: html
---

## Instructions

  - Add you name and roll number in the line 3 of YAML header. Only enter last 3 digits of roll number.
  - You exam will be considered complete and submitted only if I receive this file, on which you have worked, vis email before 5:10pm.
  - Work in this same file.
  
## Run the following code chunk:

```{r getdata}

install.packages("janitor") # only if not installed

source("https://raw.githubusercontent.com/AyushBipinPatel/bsc21-24-p1-gipe/master/create-data-26th.R")

library(tidyverse)
# feel free to  add more libraries as you need
# here in this chunk

```

## Your data

> Run th code chunk below to inspect the data you will be working on

```{r}
View(data_26)
names(data_26) # available variables
```

## Question 1 (2 marks)

>Write and execute code that will provide the total number of missing values in the column `urban_population_growth_annual_percent` in the data_26

```{r}

```

## Quesiton 2 (2 marks)

> Write and execute code that will only keep observations realted to India and Ecuador, and only after the year 2000

```{r}

```


## Question 3 (3 mark)

> In the `data_26`, there are two columns `labor_force_female_percent_of_total_labor_force` and `labor_force_total`. Use this two columns to create a new column that will record the number of males in labour force. Name this new column `labour_force_male_total`.

```{r}
data_26|>
  dplyr::filter(country_name != "World")|>
  ggplot2::ggplot(ggplot2::aes(arable_land_hectares_per_person,agricultural_land_sq_km))
```

## Question 4 (7 marks)

> Create a line chart between variable `arable_land_hectares_per_person` for India and China. Each country should be represented by a line. Colour of line should be linked to country. Add a title, caption, axes labels and theme of your choice to the plot.

```{r}

```

## Question 5 (4 marks)

> Write a code that will create a table where the minimum value for `access_to_electricity_percent_of_population` variable across all the years is recorded for every country. Arrange the table in descending order of the minimum value. 

```{r}

```

## Question 6 (4 marks)

> Write code that will change the data from wide format to long format. Do this in such a way that the columns of the final data should be :

[1] "country_name"                                                                      
[2] "country_code"                                                                      
[3] "year"

[4] "indicator_name"

[5] "value"


## Question 7 (3 marks)

> Write code that will create a table where mean as well as the median `electric_power_consumption_k_wh_per_capita` for each country is recorded.

```{r}

```

